Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-23 cav2017/cav2017.tex
squeeze description of benchmarks

\textit{DC Motor Position and Rate} plants describes the angular position and 
velocity of a DC Motor, respectively. 
\textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and 
control based on the pitch dimension. 
\textit{Ball Magnetic Levitation} plant describes a physical model that keeps a 
metal ball hanged in air via a magnetic field. 
\textit{Buck Converter} plant represents a power converter model that steps down 
voltage from the supply to the load while stepping up current. 
\textit{Boost Converter} plant also represents a power converter model, but here 
it steps up voltage from the supply to the load while stepping down current. 
\textit{Buck-boost Converter} plant represents a converter model that has an output 
voltage magnitude, which is either greater than or less than the input voltage magnitude.

\textit{Automotive Cruise System} plant represents the speed of a motor vehicle. 
\textit{Helicopter Longitudinal Motion} plant provides the longitudinal motion model 
of a helicopter. 
\textit{Inverted Pendulum} plant describes a pendulum model
with its center of mass above its pivot point. 
\textit{Magnetic Suspension} plant provides a physical model for which 
a given object is suspended via magnetic field. 
\textit{Magnetized Pointer} plant describes a physical model that is rotated through interaction 
with magnetic fields (typically employed in analogue gauges and indicators).
\textit{1/4 Car Suspension} plant presents a physical model that connects a car to its wheels 
and allows relative motion between both parts.
\textit{Computer Tape Driver} plant describes a physical model to read and write data 
on a storage device in the computer.
\textit{USCG Cutter Tampa Heading Angle} plant presents a physical model 
for the yaw angle dynamics of a US warship USCG Cutter Tampa.

All benchmarks were discretized with different sample times using 
the approach described in the Appendix~\ref{sec:appendix}. 
All experiments were performed considering $x_{i}^{-}=-1$ and 
$x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.

We have conducted the experimental evaluation on a 12-core 2.40 GHz
Intel Xeon E5-2440 with 96 GB of RAM and Linux OS. All times given are wall 
clock time in seconds as measured by the UNIX date command.

>>>>

\textit{DC Motor Position and Rate} plants describes the angular position and 
velocity of a DC Motor, respectively. 
\textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and 
control based on the pitch dimension. 
\textit{Ball Magnetic Levitation} plant describes a physical model that keeps a 
metal ball hanged in air via magnetic field. 
\textit{Buck Converter} plant represents a power converter model that steps down 
voltage from the supply to the load while stepping up current. 
\textit{Boost Converter} plant also represents a power converter model, but
it steps up voltage from the supply to the load while stepping down current. 
\textit{Buck-boost Converter} plant represents a converter model that has an output 
voltage magnitude, which is either greater than or less than the input voltage magnitude.

\textit{Automotive Cruise System} plant represents the speed of a motor vehicle. 
\textit{Helicopter Longitudinal Motion} plant provides the longitudinal motion model 
of a helicopter. 
\textit{Inverted Pendulum} plant describes a pendulum model
with its center of mass above its pivot point. 
\textit{Magnetic Suspension} plant provides a physical model for which 
a given object is suspended via magnetic field. 
\textit{Magnetized Pointer} plant describes a physical model employed in analogue gauges 
and indicators that is rotated through interaction with magnetic fields.
\textit{1/4 Car Suspension} plant presents a physical model that connects a car to its wheels 
and allows relative motion between both parts.
\textit{Computer Tape Driver} plant describes a physical model to read and write data 
on a storage device in the computer.
\textit{USCG Cutter Tampa Heading Angle} plant presents a physical model 
for the yaw angle dynamics of a US warship USCG Cutter Tampa.

All benchmarks were discretized with different sample times using 
the approach described in the Appendix~\ref{sec:appendix}. 
All experiments were performed considering $x_{i}^{-}=-1$ and 
$x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.
We have conducted the experimental evaluation on a 12-core 2.40 GHz
Intel Xeon E5-2440 with 96 GB of RAM and Linux OS. All times given are wall 
clock time in seconds as measured by the UNIX date command.
